Lecture 8: Extensive Form Games with Perfect Information

### 2014-11-04 course-game/session1/ehsan_session1.tex
changes

\documentclass{beamer}
\usepackage[latin1]{inputenc,colortbl}
\usepackage{epsfig}
\usetheme{Frankfurt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
%\newtheorem{definition}{Definition}
\title[Lecture 8: Extensive Form Games with Perfect Information]{Lecture 8: Extensive Form Games with Perfect Information}
\author{INSE 6441/2 DD\\ \vspace{0.2cm} Applied Game Theory and Mechanism Design \\ Fall 2014}
\institute{Department of Computer Science and Software Engineering\\Concordia University}
\date{Novermber 17, 2014}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame1 title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame2 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Example: Core}

@@

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties}
    \begin{itemize}
        \item The core may not always be non-empty.
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{blue}superadditive}, the Shapley value is {\color{blue}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{blue}convex}, the Shapley value is also group rational, hence, it is in the {\color{blue}core}.
        \item A convex game has a non-empty core.
        \item Core and Shapley value are combinatorial problems.
        \item There are other well-known solution concepts: Bargaining set, nucleolus and kernel.
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
        \item Example: 
        \begin{itemize}
            \item let $N={1,2,3}, C={1,2}, v({1,2})=8, x=(3,2,5)$
            \item $e(C,x)=v({1,2})-(x_1 + x_2)=8-(3+2)=3.$
        \end{itemize}
        \item We can interpret a positive excess $(e(C,x) > 0)$ as the amount of dissatisfaction or {\color{blue} complaint} of the members of $C$ from the allocation x.
        \item We can use the excess to define the core:
        \begin{itemize}
            \item $Core(N,v)=\{x \in R^n | x is an imputation and \forall C \subseteq N, e(C,x) \leq 0\}$
        \end{itemize}
        \item This definition shows that no coalition has any complaint: each coalition's demand can be granted.
    \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Nucleolus}
    \begin{itemize}
        \item Let $(N,v)$ be a $TU$ game.
        \item Let $Imp$ be the set of all imputations.
        \item The {\color{blue}$nucleolus Nu(N,v)$} is the set
        \begin{itemize}
            \item $Nu(N,v) = \{x \in Imp|\forall y \in Imp e(y)* \geq_{lex} e(x)*\}$
        \end{itemize}
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community and Web Service Interaction Model - (Phase 1)}

>>>>

\documentclass{beamer}
\usepackage[latin1]{inputenc,colortbl}
\usepackage{epsfig}
\usetheme{Frankfurt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
%\newtheorem{definition}{Definition}
\title[Lecture 8: Extensive Form Games with Perfect Information]{Lecture 8: Extensive Form Games with Perfect Information}
\author{INSE 6441/2 DD\\ \vspace{0.2cm} Applied Game Theory and Mechanism Design \\ Fall 2014}
\institute{Department of Computer Science and Software Engineering\\Concordia University}
\date{Novermber 6, 2014}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame1 title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame2 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Example 1: Vector game}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Example 2: Three-player majority game}
    \begin{center}
      $N = \{1,2,3\}$ \\
      $v(\{i\}) = 0,$\\
      $v(\{C\}) = 0, for |C| = 2$ \\
      $v(N) = 1$ \\
    \end{center}
    \[ (x_1, x_2, x_3) \in Core(N,n) \iff \left\{
      \begin{array}{l l}
        x_i \geq 0 & \quad \forall i \in N\\
        x_i + x_j \geq \alpha & \quad \forall(i,j) \in N^2 i \neq j\\
        \sum_{i \in N} x_i = 1 &
      \end{array} \right.\]
    \[ (x_1, x_2, x_3) \in Core(N,n) \iff \left\{
      \begin{array}{l l}
        0 \leq x_i \leq 1 - \alpha & \quad \forall i \in N\\
        \sum_{i \in N} x_i = 1 &
      \end{array} \right.\]

    $Core(N,v)$ is nonempty $iff \alpha \leq \frac{2}{3}$ \\

    \begin{itemize}
        \item The core may not be fair: the core only considers stability. \\
        \item The core may not have an answer!
    \end{itemize}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} {Example: Glove game}
    The {\color{blue}glove game} is a coalitional game where the players have left and right hand gloves and the goal is to form pairs
    \begin{center}
      $N = \{1,2,3\}$ \\
    \end{center}
    where players 1 and 2 have right hand gloves and player 3 has a left hand glove.
    \[ v(S) = \left\{
      \begin{array}{l l}
        1 & \quad if \quad S \in \{\{1,3\},\{2,3\},\{1,2,3\}\} \\
        0 & \quad otherwise        
      \end{array} \right.\]      
    $S = \emptyset, v(\{1\}) - v(\emptyset) = 0 - 0 = 0$ \\    
    $S = \{2\}, v(\{1,2\}) - v(\{2\}) = 0 - 0 = 0$ \\
    $S = \{3\}, v(\{1,3\}) - v(\{3\}) = 1 - 0 = 1$ \\
    $S = \{2,3\}, v(\{1,2,3\}) - v(\{2,3\}) = 1 - 1 = 0$ \\            
    \begin{itemize}
        \item ${\color{blue}x_1} = 0 + 0 + \frac{1}{6} + 0 = \frac{1}{6}$, ${\color{blue}x_2} = \frac{1}{6}$, ${\color{blue}x_3} = \frac{2}{3}$    
        \item ${\color{blue}x} = (\frac{1}{6}, \frac{1}{6}, \frac{2}{3})$
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties}
    \begin{itemize}
        \item The core may not always be non-empty.
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{blue}superadditive}, the Shapley value is {\color{blue}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{blue}convex}, the Shapley value is also group rational, hence, it is in the {\color{blue}core}.
        \item A convex game has a non-empty core.
        \item Core and Shapley value are combinatorial problems.
        \item There are other well-known solution concepts: Bargaining set, nucleolus and kernel.
    \end{itemize}
\end{frame}

@@

    \begin{itemize}
        \item Example:
        \begin{itemize}
            \item let $N={1,2,3}, C={1,2}, v({1,2})=8, x=(3,2,5)$
            \item $e(C,x)=v({1,2})-(x_1 + x_2)=8-(3+2)=3.$
        \end{itemize}
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Excess of a coalition}

    \begin{itemize}
        \item We can interpret a positive excess $(e(C,x) > 0)$ as the amount of dissatisfaction or {\color{blue} complaint} of the members of $C$ from the allocation x.
        \item We can use the excess to define the core:
        \begin{center}
            $Core(N,v)=\{x \in R^n |$ $x$ $is$ $an$ $imputation$ $and$ $\forall C \subseteq N, e(C,x) \leq 0\}$
        \end{center}
        \item This definition shows that no coalition has any complaint: each coalition's demand can be granted.
    \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Nucleolus}
    \begin{itemize}
        \item Let $(N,v)$ be a $TU$ game.
        \item Let $Imp$ be the set of all imputations.
        \item The {\color{blue}$nucleolus$ $Nu(N,v)$} is the set:
        \begin{itemize}
            \item $Nu(N,v) = \{x \in Imp|\forall y \in Imp e(y)* \geq_{lex} e(x)*\}$
        \end{itemize}
    \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community and Web Service Interaction Model}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community and Web Service Interaction Model}
